---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# apa.cor - A correlation matrix in R, using APA style

![GitHub last commit](https://img.shields.io/github/last-commit/ggluca/apa.cor?logo=bitcoin&style=plastic)

## What it does:

This single-function package is designed to be a fast way of creating a correlation matrix from a dataframe that includes the needed variables. It also produces means, standard deviations and NHS significance tests at various levels, with an export function for the clipboard.

It is also a good tool of creating an S3 object that plugs in well into the `papaja: Prepare APA Journal Articles with R Markdown` package, to produce a correlation table afer the APA manuscript guidelines.

# Installation

To install the latest (see latest changes below), type the following commands into the R console:

```{r, eval=FALSE}
library(devtools)
devtools::install_github("GGLuca/apa.cor")
```

## Example of Recommended Usage

To create a correlation matrix for the Agreeableness items from the `bfi`dataset (`psych` package, 25 Personality items representing 5 factors):

```{r, message=FALSE}
library(tidyverse)    # load Tidyverse
library(psych)        # load package psych for the `bfi`dataset
library(apa.cor)

bfi %>% 
  select(A1:A5) %>% 
  apa.cor()
```

## Supplemental Argument

The function also has an export option `export = TRUE`, that copies the output into the clipboard, for further manipulation such a simple paste into Microsoft Word.

```{r eval=FALSE}
apa.cor(x, export = TRUE)
```

## Better usage

Since the function outputs a proper S3 object, it is perfect for integrating it into the [papaja](https://github.com/crsh/papaja) package, be it to create html tables or better yet, beautifully formatted PDF files.

```{r, warning=FALSE, message=FALSE, fig.cap="Table 1"}
library(papaja)

bfi %>% 
  select(A1:A5) %>% 
  apa.cor() %>% 

apa_table(
  .,
  , caption = "Variable Means, Standard Deviations, and Correlations Between Agreeableness Items"
  , note = "This table was created with apa_table()."
  , escape = TRUE
)
```

